% English resume (one page). Build: pdflatex Resume_EN.tex (twice)
\documentclass[9pt,letterpaper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=0.5in, top=0.48in, bottom=0.48in]{geometry}
\usepackage{hyperref}
\usepackage{tabularx}

\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue, pdfauthor={Diyuan Deng}, pdftitle={Resume - Diyuan Deng}}

\newcommand{\FullName}{Diyuan Deng}
\newcommand{\Email}{diyuandeng@link.cuhk.edu.cn}
\newcommand{\Phone}{+86~153~0153~9901}
\newcommand{\Location}{Shenzhen, China}
\newcommand{\Github}{https://github.com/aCm1T}
\newcommand{\LinkedIn}{https://www.linkedin.com/in/diyuandeng/}

% Section: fixed spacing (no stretch glue that leaves random gaps)
\newcommand{\cvsec}[1]{%
  \par\addvspace{0.32em}%
  \noindent{\normalsize\bfseries #1}\\[-0.22em]%
  \rule{\linewidth}{0.4pt}%
  \par\vspace{0.14em}%
}

\newcolumntype{Y}{>{\raggedright\arraybackslash}X}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\leftmargini}{1.05em}
\setlength{\itemsep}{0.03em}
\setlength{\parsep}{0pt}
\setlength{\topsep}{0.05em}
\setlength{\partopsep}{0pt}
\linespread{1.05}\selectfont

\begin{document}
\raggedright

\begin{center}
  {\Large\bfseries \FullName}\\[0.15em]
  {\footnotesize B.Sc.\ candidate, Data Science \& Big Data Technology {\textbar} embodied AI, LLM inference, applied ML}\\[0.2em]
  \scriptsize
  \href{mailto:\Email}{\Email} \quad|\quad \Phone \quad|\quad \Location \quad|\quad \href{\Github}{GitHub} \quad|\quad \href{\LinkedIn}{LinkedIn}
\end{center}
\vspace{0.08em}

\cvsec{Education}
\textbf{The Chinese University of Hong Kong, Shenzhen (CUHK-Shenzhen)} \hfill {\normalsize Shenzhen, China}\\
B.Sc., Data Science and Big Data Technology \hfill {\normalsize Sept.\ 2023 -- Jun.\ 2027 (expected)}
\begin{itemize}
  \item GPA: \textbf{3.43} / 4.0.
  \item Coursework: Database Systems, Algorithm Design and Analysis, Stochastic Processes, Optimization, Machine Learning, Statistical Computing.
\end{itemize}

\cvsec{Experience}
\textbf{Data Engineering Intern} \quad Shanghai Wuzhi Evolution Technology Co., Ltd., Embodied Data R\&D \hfill {\normalsize Shanghai {\textbar} Jun.--Aug.\ 2025}\\
{\small Collaborated with Prof.\ Bo Zhao's group (Shanghai Jiao Tong University) on embodied AI data and VLA models.}
\begin{itemize}
  \item \textbf{xArm} data pipeline and \textbf{VLA} optimization; \textbf{10,000+} trajectories. \textbf{LeRobot} stack; multimodal LLMs and NL commands; grasping/stacking \textbf{$>$90\%} success.
\end{itemize}

\cvsec{Projects \& Research}
\textbf{Enterprise LLM Inference (SFGlang)} \quad Core Developer, SF Technology Co., Ltd. \hfill {\normalsize Jan.\ 2026 -- Present}
\begin{itemize}
  \item Throughput/comm for \textbf{Qwen3}-class LLMs and multimodal (\textbf{4B / 30B}) under enterprise load.
  \item \textbf{SGLang}, dual-container; \textbf{4090} (\textbf{PD/EPD}, \textbf{TP/DP/EP}, \textbf{FP8/INT8}); load-test platform; \textbf{two} patents (in progress). \textbf{Qwen-30B} \textbf{TP4+DP2}: \textbf{TTFT $-$48.9\%}, \textbf{+664\%} throughput; \textbf{Qwen-4B} \textbf{TP1+DP2}: \textbf{+750\%}.
\end{itemize}

\vspace{0.06em}
\noindent\textbf{NSC-Advisor --- Ischemic Stroke Prognosis} \quad Research Assistant \hfill {\normalsize Sept.--Dec.\ 2025}\\
{\footnotesize Related work submitted to \textbf{ISMRM} (under review).}
\begin{itemize}
  \item Interpretable prognosis (\textbf{favorable vs.\ unfavorable}) from admission data; few-shot, prompting, \textbf{RAG}. Dual-input UI; \textbf{93.75\%} on \textbf{16} held-out cases.
\end{itemize}

\vspace{0.06em}
\noindent\textbf{Library Management System} \quad Developer \hfill {\normalsize Sept.--Nov.\ 2024}
\begin{itemize}
  \item Full-stack \textbf{Python (tkinter) + SQLite}: four normalized tables, composite indexes, \textbf{15+} features (\textbf{SHA-256} authentication), admin dashboard; tests covered \textbf{100\%} of requirements.
\end{itemize}

\vspace{0.06em}
\noindent\textbf{2D RPG Combat (UE5 + C++)} \quad Developer \hfill {\normalsize Sept.--Dec.\ 2024}
\begin{itemize}
  \item \textbf{C++} combat (three enemy AI types); \textbf{Qt} launcher with \textbf{SHA-256} messaging; \textbf{PaperZD} animation state machines; team \textbf{1,000+} lines core code; \textbf{best course project}.
\end{itemize}

\cvsec{Campus Roles, Honors \& Skills}
\textbf{Undergraduate Teaching Fellow (USTF)}, School of Data Science \hfill {\normalsize Sept.\ 2024 -- Present}
\begin{itemize}
  \item \textbf{Data Structures}, \textbf{Databases}, +1 core course; \textbf{10+} tutorials, \textbf{800+} students; co-designed problems and grading; \textbf{SDS Excellent USTF Award} (2024--2025).
\end{itemize}

\vspace{0.08em}
\noindent\textbf{Student Assistant}, University Library \hfill {\normalsize Nov.\ 2023 -- Present}
\begin{itemize}
  \item Printers (\textbf{X1E}, \textbf{Ultimaker S5}, \textbf{Form~2}), \textbf{30+} jobs; \textbf{10+} edits (FCP, Photoshop); 3D-printing workshops.
\end{itemize}

\vspace{0.08em}
\noindent\textbf{Founder \& Vice President}, 2Tired Cycling Club \hfill {\normalsize Jul.\ 2024 -- Present}
\begin{itemize}
  \item Core team \textbf{20}, five functions; Songshan Lake \& Tour de France meet-up; first year \textbf{80+} members, \textbf{95\%} satisfaction.
\end{itemize}

\vspace{0.1em}
\noindent\textbf{Honors:}\ {\small CUMCM Guangdong Third (2025); bronze 1500\,m (university games); bronze 100\,m breaststroke (sports festival).}

\vspace{0.2em}
\noindent\small
\begin{tabularx}{\linewidth}{@{}p{3.45em}Y@{}}
  \textbf{Languages} & Chinese (native); English (professional proficiency for coursework and work). \\[0.06em]
  \textbf{Technical} & \textbf{Python} (advanced), \textbf{SQL}; C++, R, \textbf{UE5}; LLM serving (SGLang, parallelism, quantization); data engineering. \\[0.06em]
  \textbf{Interests} & Cycling, photography, hiking, amateur radio, Model United Nations. \\
\end{tabularx}

\end{document}
